ms_borrador

### 2018-01-18 analysis/rwi/climate_rwi_relate.Rmd
update figures

---
title: "Climate-RWI relations"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output:
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---

>>>>

---
title: "Climate-RWI relations"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Dec"
output:
  md_document:
    variant: markdown_github
bibliography: ../refs/references.bib 
csl: ../refs/ecology.csl
---

### 2018-01-18 man/ms_2_results.Rmd
update figures

#### Resilience metrics EVI

Pyrenean oak forests showed significantly lower resistance to 2005 drought event than to 2012 one [2005: 0.858 (0.853-0.863); 2012: 0.943 (0.939 - 0.947); table R1; Figura R4a, F = 799.86, p <0.0001]. The 2005 drought reduced the greenness of oak to 85.8 % while the 2012 reduced 94.3 %. Southern populations showed significantly higher values of resistance to drought than northern ones, except for 2012 where non-significant differences were recorded (table R1, Figure R4a).

@@

The oak forests recovered their greenness more rapidly after the 2005 drought than after 2012. In the period after 2005 drought, greeness achieved was 112 % (Rc = 1.12) and after 2012 105.7 % (Rc = 1.057). A similar recovery after the 2005 and 2012 drought event was observed for southern populations (p = 0.2453; Figure R4), whilst the northern populations showed a significantly greater recovery after the 2005 drought than after the 2012 drought.

@@

table R1. Robust anovas con F-Values 
Figura R2. Interaction plot resilience metrics

@@

## Resiliencia BAI

Although no significant differences were observed in the resistance of the oak growth to both drought events (F = 6.0189; p = 0.019; table R2; Figura R5), the 2005 drought reduced growth more than 2012 did (Rt = 0.721 and 0.819 respectively). Northern population showed resistance values lower than southern ones, especially for 2005 drought event where the growth was reduced to 44.5 % of the preceding period.

>>>>

## Responses to drougth: greenness

*Q. pyrenaica* forest showed significantly lower resistance to 2005 drought event than to 2012 one [2005: 0.858 (0.853-0.863); 2012: 0.943 (0.939 - 0.947); table 2; Figure 3a, F = 799.86, p <0.0001]. The 2005 drought reduced the greenness of oak to 85.8 % while the 2012 reduced 94.3 % (tabla rs1 quizás, duda en esto). Southern populations showed significantly higher values of resistance to drought than northern ones, except for 2012 where non-significant differences were recorded (Figure 3a).

@@

The oak forests recovered their greenness more rapidly after the 2005 drought than after 2012. In the period after 2005 drought, greeness achieved was 112 % (Rc = 1.12) and after 2012 105.7 % (Rc = 1.057). A similar recovery after the 2005 and 2012 drought event was observed for southern populations (p = 0.2453; Figure 3a), whilst the northern populations showed a significantly greater recovery after the 2005 drought than after the 2012 drought.

@@

Figura R2. Interaction plot resilience metrics

@@

## Responses to drougth: tree-growth (BAI)

Although no significant differences were observed in the resistance of the oak growth to both drought events (F = 6.0189; p = 0.019; table 2; Figure 3b), the 2005 drought reduced growth more than 2012 did (Rt = 0.721 and 0.819 respectively). Northern population showed resistance values lower than southern ones, especially for 2005 drought event where the growth was reduced to 44.5 % of the preceding period.

### 2018-01-18 man/ms_figures.Rmd
update figures

![](../out/fig/geomap/mapa_situacion.jpg)

@@

Figure 2. Profile of montly EVI values for *Q. pyrenaica* forests during the 2005 (*green*) and 2012 (*blue*) drought events and for the reference period (*gray*) (a). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b).

Comparison of EVI profile for the reference period (*grey*) and the 2005 (*green*) and 2012 (*blue*) drought events

### Figure R2 = 3 
```{r}
mhuber <- read.csv(here("/out/anovas_resilience/huber_evi", "robust_mhuber.csv"), header = TRUE)

# NO plot rrs 
mhuber_filter <- mhuber %>% filter(var != 'rrs')

pd <- position_dodge(.2)

robust_plot_evi_drought <-
  ggplot(mhuber_filter, 
         aes(x = as.factor(disturb_year), y = M.Huber, 
             color = site, 
             group = site, 
             fill = site)) +
  geom_errorbar(
    aes(ymin = lower.ci, ymax = upper.ci),
    width = .1, size = 0.7, position = pd) +
  geom_line(aes(group = site, color = site, linetype = site), position = pd) +
  geom_point(shape = 21, size = 2.5, position = pd) +
  geom_text_repel(aes(label=Letter), 
                  nudge_x = 0.3, size = 5,
                  segment.size = 0) +
  facet_wrap(
    ~var_sorted, nrow = 1, scales = "free_y",
    labeller = as_labeller(c(
      "0_rt" = "Resistance",
      "1_rc" = "Recovery",
      "2_rs" = "Resilience"))) +
  scale_color_manual(values = c("black", "blue")) +
  scale_fill_manual(values = c("black", "blue")) + theme_bw() +
  scale_linetype_manual(values = c("solid", "dashed")) +
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    legend.position = "bottom") +
  ylab("") + xlab("Drought event")

robust_plot_evi_drought 
```

>>>>

![](../out/fig/geomap/mapa_situacion.jpg){height=600px}

@@

Figure 2. Comparison of EVI profile for the reference period (*gray*) and during the 2005 (*green*) and 2012 (*blue*) drought events (a). EVI standardized anomaly ($EVI~sa$) during the period 2000-2016 for northern and southern populations (b).

### Figure 3

```{r}
mhuber <- read.csv(here("/out/anovas_resilience/huber_evi", "robust_mhuber.csv"), header = TRUE)
mhuberbai <- read.csv(here("/out/anovas_resilience/huber_bai", "robust_mhuber.csv"), header = TRUE)

# NO plot rrs 
mhuber_filter <- mhuber %>% filter(var != 'rrs') %>% mutate(disturb_year = as.factor(disturb_year))
mhuberbai_filter <- mhuberbai %>% filter(var != 'rrs') %>% mutate(disturb_year = as.factor(disturb_year))

pd <- position_dodge(.2)
line_lwd <- .8

aes_disturb <- aes(x = disturb_year, y = M.Huber, color = site, group = site, fill = site)
aes_site <- aes(x=site, y=M.Huber, color = disturb_year, group=disturb_year, fill=disturb_year)

theme_res_site  <- list(
  geom_errorbar( 
    aes(ymin = lower.ci, ymax = upper.ci, linetype=disturb_year),
    width=.2, position=pd, lwd=line_lwd),
  geom_line(aes(group = disturb_year, color = disturb_year, linetype = disturb_year), position = pd, lwd=line_lwd), 
  geom_point(shape = 21, size = 2.5, position = pd), 
  geom_text_repel(aes(label=Letter), 
                  nudge_x = 0.3, direction="both", 
                  size = 5, show.legend = FALSE,
                  segment.size = 0.7, 
                  segment.alpha = 0.5),
  facet_wrap(
    ~var_sorted, nrow = 1, scales="free_y",
    labeller = as_labeller(c(
      "0_rt" = "Resistance",
      "1_rc" = "Recovery",
      "2_rs" = "Resilience"))),
  theme_bw(), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),  
  ylab("Response value"), 
  xlab("")
)

theme_res_disturbyear  <- list(
  geom_errorbar( 
    aes(ymin = lower.ci, ymax = upper.ci, linetype=site),
    width=.2, position=pd, lwd=line_lwd),
  geom_line(aes(group = site, color = site, linetype = site), position = pd, lwd=line_lwd), 
  geom_point(shape = 21, size = 2.5, position = pd), 
  geom_text_repel(aes(label=Letter), 
                  nudge_x = 0.3, direction="both", 
                  size = 5, show.legend = FALSE,
                  segment.size = 0.7, 
                  segment.alpha = 0.5),
  facet_wrap(
    ~var_sorted, nrow = 1, scales="free_y",
    labeller = as_labeller(c(
      "0_rt" = "Resistance",
      "1_rc" = "Recovery",
      "2_rs" = "Resilience"))),
  theme_bw(), 
  theme(
    panel.grid.minor = element_blank(),
    strip.background = element_rect(
      colour = "black",
      fill = "white"),
    plot.title = element_text(hjust = -0.05, size = 16, margin = margin(t=-5, b=1))),  
  ylab("Response value"), 
  xlab("")
)

theme_res_evi <-  list(
  scale_color_manual(values = c("black", "blue")),
  scale_shape_manual(values=c(19, 22)),
  scale_fill_manual(values = c("black", "blue")),
  scale_linetype_manual(values = c("solid", "solid"))
)

theme_res_bai <- list(
  scale_color_manual(values=c('black','blue','blue')), 
  scale_shape_manual(values=c(19, 22, 15)),
  scale_fill_manual(values=c('black','white','blue')),  
  scale_linetype_manual(values=c("solid", "solid", 'solid'))
)

```

```{r}
res_evi_drought <-
  ggplot(mhuber_filter, aes_disturb) +
  theme_res_disturbyear + 
  theme_res_evi +
  theme(legend.position='top') + 
  ggtitle("a) EVI")

res_bai_drought <-
  ggplot(mhuberbai_filter, aes_disturb) + 
  theme_res_disturbyear + 
  theme_res_bai + 
  theme(legend.position='bottom') + 
  xlab('Drought event') + 
  ggtitle("b) BAI")
```

```{r, fig.height=7}
res_evi_drought  + res_bai_drought + plot_layout(ncol=1)
```

Figure 3. Response of northern (*black*) and southern (*blue*) populations of *Q. pyrenaica* forests to drougth in terms of resistance, recovery and resilience of greenness (EVI; a) and tree growth (BAI; b) for the years 2005 and 2012.

### Figure 4
```{r}
res_evi_site <-
  ggplot(mhuber_filter, aes_site) +
  theme_res_site + 
  theme_res_evi + theme(legend.position='top') + 
  ggtitle("a) EVI")

res_bai_site <-
  ggplot(mhuberbai_filter, aes_site) + 
  theme_res_site + 
  theme_res_bai + 
  theme(legend.position='bottom') + 
  xlab('Drought event') + 
  ggtitle("b) BAI")
```

```{r, fig.height=7}
res_evi_site  + res_bai_site + plot_layout(ncol=1)
```

### 2018-01-18 man/report.Rmd
update figures

---
title: "ms_borrador"
author: "AJ Perez-Luque; G. Gea-Izquierdo; R. Zamora; FJ. Bonet"
date: "2017"
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: template_ms.docx
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

>>>>

---
title: "ms_borrador"
author: "AJ Perez-Luque; G. Gea-Izquierdo; R. Zamora; FJ. Bonet"
date: "2017"
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: template_ms.docx
bibliography: ../refs/references.bib
csl: ../refs/ecology.csl
---

@@

```{r child = 'ms_supp.Rmd'}
```
